Overconfidence and settlement: evidence from Mexican labor courts\thanks{We would like to thank Sebastian Garcia, Isaac Meza, Diana Roman, and Monica Zamudio (``la banda pesada'' and ``los mas aca'') for superhuman research assistance. All errors are ours.}

### 2017-08-17 Paper/main.tex
Primer pendiente

\begin{table}[H]
    \caption{Baseline expectations comparison between parties}
    \label{Table_expectations_plaintiff_defendant}
    \begin{center}
       \scriptsize{\input{./Tables/SS_B.tex}}
    \end{center}
    \footnotesize    
    \textit{Notes: Summary statistics on parties' beliefs, conditioning on having survey data for both parties. Since there are few observations for which both client and lawyer answered the survey, we take a simple average whenever that is the case.}

@@

%#include
\begin{table}[H]
    \caption{Amount asked (log), amount won (log), and probability of winning }
    \label{Table_Reg_winnings_log}
    \begin{center}
        \scriptsize{\input{./Tables/TableReg1_log.tex}}
    \end{center}
    \footnotesize
    \textit{Notes: Regression of amounts (in log pesos) asked (in log pesos) asked/won ratio and prob. of winning, by outcome (only basic variables included).} 
    \textit{Do file: } \texttt{reg\_amount.do}
\end{table}

@@

\begin{landscape}
%#include
\begin{table}[H]
\caption{Determinants of overconfidence}
\label{Table_determinantsOC}
\begin{center}
\scriptsize{\input{./Tables/OC_reg.tex}}
\end{center}
 \footnotesize
\textit{Notes:} 
\emph{Mistreated} variable refers to the survey question: "How well do you think you were treated by the firm?". The omitted category is "Very Good", while 1, 2 and 3 refer to "Fairly Well", "Not so well" and "Not well at all".
Omited variable for \emph{education} is elementary education, while for \emph{Mistreated} is very good, and the scale is increasing, i.e. the worker feels more mistreated . We use a measure of relative overconfidence which is the \textit{percentage} quantity expected over the calculators prediction.
\textit{Do file: } \texttt{oc\_reg.do oc\_reg\_B.do}
\end{table}

@@

\begin{table}[H]
\caption{Determinants of updating (Theta)}
\label{Table_determinants_updating}
\begin{center}
\scriptsize{\input{./Tables/oc_reg_theta.tex}}
\end{center}
 \footnotesize
\textit{Notes:} 
\emph{Mistreated} variable refers to the survey question: "How well do you think you were treated by the firm?". The omitted category is "Very Good", while 1, 2 and 3 refer to "Fairly Well", "Not so well" and "Not well at all".
Omited variable for \emph{education} is elementary education, while for \emph{Mistreated} is very good, and the scale is increasing, i.e. the worker feels more mistreated . Theta updating refers to the following statistic: $\theta=\left|\frac{P-exitsurvey}{P-initialsurvey}\right|$. Where $P$ is the prediction made by the calculator and $exit$ and $initial$ survey variables denote what each part answered on the survey for amount won. Note that when $\theta=1$ we have no update with respect to the prediction. And when $\theta<1$ they update in the direction of what calculator says. The extreme case $\theta=0$ implies perfect updating with respect to what the calculator says. 
\textit{Do file: } \texttt{oc\_reg\_theta.do}
\end{table}

\begin{table}[H]
\caption{Determinants of updating (Relative)}
\label{Table_determinants_updating}
\begin{center}
\scriptsize{\input{./Tables/oc_reg_rel.tex}}
\end{center}
 \footnotesize
\textit{Notes:} 
\emph{Mistreated} variable refers to the survey question: "How well do you think you were treated by the firm?". The omitted category is "Very Good", while 1, 2 and 3 refer to "Fairly Well", "Not so well" and "Not well at all".
Omited variable for \emph{education} is elementary education, while for \emph{Mistreated} is very good, and the scale is increasing, i.e. the worker feels more mistreated. Relative updating is computed as $\frac{exitsurvey-initialsurvey}{initialsurvey}$.
\textit{Do file: } \texttt{oc\_reg\_theta.do}
\end{table}
\end{landscape}

@@

%#include
\begin{table}[H]
    \caption{Treatment Effects by months after treatment}
    \label{Table_effects_F}
    \begin{center}
    \scriptsize{\input{./Tables/minicortes_monthstreatment.tex}}
    \end{center}
    \footnotesize
    \textit{Notes:} 
    Calc=Conc and Calc=Conc=0 shows the p-value for the respective tests.
    \textit{Do file: } \texttt{minicortes\_monthstreatment.do}
\end{table}

@@

@@

\begin{figure}[H]
    \caption{Percent that know main legal constitutional entitlement}
    \label{Knowindemfig}
    \begin{center}
        \begin{subfigure}{0.49\textwidth}
            \caption{Employee claims to know}
            \centering
            \includegraphics[width=\textwidth]{Knows.pdf}
        \end{subfigure}
        \begin{subfigure}{0.49\textwidth}
            \caption{Employee correctly knows }
                \centering
                \includegraphics[width=\textwidth]{Correctly_knows.pdf}
        \end{subfigure}
        \end{center}
    {\footnotesize \textit{Notes: } This is based on the subject's answer to two questions: 7.01: "In case of an unjustified firing, the law grants you to get a severance pay stipulated in the Constitution. Do you know how many days of your salary does this account for?" and "7:02: How many days of your salary does this pay account for?". First panel correspond to the first question while second panel to the second one.}
    {\footnotesize \textit{Do file: } \texttt{knowledge\_emp.do}}
\end{figure}

\begin{figure}[H]
    \caption{Knowledge about their own claims in lawsuit}
    \label{Knowtheirclaimsfig}
    \begin{center}
        \begin{subfigure}{0.49\textwidth}
            \caption{Const. compensation}
            \centering
            \includegraphics[width=\textwidth]{Compensation.pdf}
        \end{subfigure}
        \begin{subfigure}{0.49\textwidth}
            \caption{SARIMSS}
                \centering
                \includegraphics[width=\textwidth]{Insurance.pdf}
        \end{subfigure}
        \begin{subfigure}{0.49\textwidth}
            \caption{Reinstatement}
            \centering
            \includegraphics[width=\textwidth]{Reinstatement.pdf}
        \end{subfigure}
            \hfill
        \begin{subfigure}{0.49\textwidth}
            \caption{Overtime}
            \centering
            \includegraphics[width=\textwidth]{Extra_hrs.pdf}
        \end{subfigure}
        \begin{subfigure}{0.49\textwidth}
            \caption{End of year bonus}
            \centering
            \includegraphics[width=\textwidth]{Holiday_bonus.pdf}
        \end{subfigure}
            \hfill
        \begin{subfigure}{0.49\textwidth}
            \caption{Sunday bonus}
            \centering
            \includegraphics[width=\textwidth]{Sunday_bonus.pdf}
        \end{subfigure}
    \end{center} 
        \footnotesize \textit{Notes: Percentage of subjects who correctly answered to the question regarding elements of their claim, by type of benefit asked.}
        {\footnotesize \textit{Do file: }  \texttt{knowledge\_lawsuit.do}}
\end{figure}

\begin{figure}[H]
    \caption{Differences in claims and compensation by case file outcome}
    \label{claimsvsoutcomes}
    \begin{center}
        \includegraphics[width=0.7\textwidth]{Amountasked.tiff}
        \end{center}
    \footnotesize \textit{Notes: This graph shows the average amount (in thousand pesos) asked, won (overall and conditional on winning), minimum legal compensation, and minimum legal compensation plus lost wages, by outcome. The bottom legend shows the percentage of cases with each outcome for our database (N=5005). Note that, by definition, workers have no chance of recovery in drops and expiries. In our data, all settlements imply a positive recovery for the worker; finally, \textbf{for judgments, only 24\% of the time does the worker recover anything.}} 
    {\footnotesize \textit{Script: } \texttt{amount\_plots.R}}
\end{figure}

\begin{figure}[H]
    \caption{Delay of case by type of conclusion}
    \label{DurationFig}
    \begin{center}
        \includegraphics[width=0.7\textwidth]{Duracion.pdf}
        \end{center}
    {\footnotesize \textit{Notes: Length of the case (in years) , by conclusion. Naturally, laudos (adjudication cases) have much higher duration than settlement cases (convenios).}}
    {\footnotesize \textit{Do file: } \texttt{length\_case.do}}
\end{figure}

\begin{figure}[H]
    \caption{Difference in what actor says and calculator predicts in amount and probability.}
    \label{Figure_overconfidence_exp}
    \begin{center}
    \begin{subfigure}{0.49\textwidth}
        \caption{Employee}
        \centering
        \includegraphics[width=\textwidth]{difference_amount_employee.pdf}
    \end{subfigure}
     \begin{subfigure}{0.49\textwidth}
        \centering
        \includegraphics[width=\textwidth]{difference_prob_employee.pdf}
    \end{subfigure}
    \begin{subfigure}{0.49\textwidth}
        \caption{Employee Lawyer}
        \centering
        \includegraphics[width=\textwidth]{difference_amount_employeelawyer.pdf}
        \end{subfigure}
          \begin{subfigure}{0.49\textwidth}
        \centering
        \includegraphics[width=\textwidth]{difference_prob_employeelawyer.pdf}
    \end{subfigure}
        \begin{subfigure}{0.49\textwidth}
            \caption{Firm Lawyer}
            \centering
            \includegraphics[width=\textwidth]{difference_amount_firmlawyer.pdf}
    \end{subfigure}
    \begin{subfigure}{0.49\textwidth}
            \centering
            \includegraphics[width=\textwidth]{difference_prob_firmlawyer.pdf}
        \end{subfigure}
    \end{center}
     \footnotesize \textit{Notes: Difference (in thousand pesos for amounts, percentage points for probabilities) from what the subject expects vs. what our models predict. Note how, for Employee and employee lawyer, the distribution for amounts is much more skewed to the right than for firm lawyers. This is only natural, since the formers are thinking about expected wins and the latters about expected losses.} 
      \footnotesize{ \textit{Do file: }  \texttt{oc\_comparison\_B.do}}
\end{figure}

\begin{figure}[H]
   \caption{Experiment flowchart}
   \label{treatment_flowchart}
    \begin{center}
    \includegraphics[width=0.42\textwidth]{./Figuras/Experiment_flowchart.png}
    \end{center}
    \footnotesize
    \textit{Notes: this flowchart shows what happened when subjects arrived to the court.}
\end{figure}

\begin{figure}[H]
    \caption{Calculator treatment format (example)}
    \label{calc_template}
    \begin{center}
        \includegraphics[width=0.9\textwidth]{calctreat.png}
        \end{center}
        {\footnotesize \textit{Notes: An example of the format shown to subjects in calculator treatment group. It shows some data on the worker, the minimum legal amount she deserves for different types of benefits, a small note on average trial duration, and calculator results: probability for each conclusion outcome, average duration and amount won (both conditional on each outcome).}}
\end{figure}

@@

\begin{table}[H]
    \caption{Summary statistics table by end mode }
    \label{tab:SS}
    \begin{center}
        \tiny{\input{./Tables/SS_bymodotermino.tex}}
    \end{center}
    \footnotesize
    \textit{Notes:} 
Summary stats of outcomes, basic and strategic variables by end mode.
    \textit{Do file: } \texttt{Table\_SS\_bymodotermino.do}
\end{table}

\begin{table}[H]
    \caption{Baseline Expectations}
    \label{Table_expectations}
    \begin{center}
       \scriptsize{\input{./Tables/SS_A.tex}}
    \end{center}
    \footnotesize    
    \textit{Notes:} 
    Summary statistics of parties' beliefs. We show mean and standard deviation for the whole sample, \& dividing by type of employee's lawyer.
    \textit{Do file: } \texttt{Table\_SS.do  Table\_SS\_bylawyer.do}
\end{table}

@@

\begin{table}[H]
    \caption{Who showed up }
    \label{whoshowedup}
    \begin{center}
        \scriptsize{\input{./Tables/Showed_up.tex}}
    \end{center}
    \footnotesize
    \textit{Notes:} 
We show some stats of who goes to the court. This is important since we can only give the treatment to the parties who go.  We decompose this in all the possible combination of show up: we use E,L,F,D subscripts to denote the different parties E: Employee; L: Employee’s Lawyer;  F: Firm; D: Firm’s Lawyer.
    \textit{Do file: } \texttt{showed\_up.do}
\end{table}

%#appendix
\begin{table}[H]
    \caption{Conciliation by type of lawyer}
    \label{tab:reg_con_oc}
    \begin{center}
        \scriptsize{\input{./Tables/concilio_vs_lawyer.tex}}
    \end{center}
    \footnotesize
    \textit{Notes:} 
   Specification (1) refers to basic variables while (2) includes all strategic variables.
    \textit{Do file: } \texttt{con\_lawyer.do}
\end{table}

@@

%#appendix 
\begin{table}[H]
    \caption{Correlation conciliation vs overconfidence - Pilot data}
    \label{Table_concvsoc}
    \begin{center}
        \scriptsize{\input{./Tables/Reg_con_oc.tex}}
    \end{center}
    \footnotesize
    \textit{Notes:} 
    All measures of OC are relative. Elastictity : Con-OC measures how much does conciliation change when overconfidence changes in 1 standard deviation. Elasticity SD:Con-OC measures how many standard deviations conciliation changes when  overconfidence changes in 1 standard deviation.
    \textit{Do file: } \texttt{corr\_con\_oc.do corr\_con\_oc\_B.do}
\end{table}

\begin{table}[H]
    \caption{Correlation conciliation vs update - Pilot data}
    \label{Table_concvsoc_theta}
    \begin{center}
        \scriptsize{\input{./Tables/Reg_con_oc_theta.tex}}
    \end{center}
    \footnotesize
    \textit{Notes:} 
   We use the following statistic to measure updating: $\theta=\left|\frac{P-exitsurvey}{P-initialsurvey}\right|$. Where $P$ is the prediction made by the calculator and $exit$ and $initial$ survey variables denote what each part answered on the survey for amount won.. Elastictity : Con-OC measures how much does conciliation change when overconfidence changes in 1 standard deviation. Elasticity SD:Con-OC measures how many standard deviations conciliation changes when  overconfidence changes in 1 standard deviation.
    \textit{Do file: } \texttt{con\_vs\_oc\_theta.do}
\end{table}

@@

\begin{table}[H]
   \caption{Treatment description}
    \label{treatment_description}
    \begin{center}
    \scriptsize{\input{./Tables/Experiment_description2.tex}}
    \end{center}
    \footnotesize
    \textit{Notes: This is a short description of the kind of treatment received by each treatment group.} 
\end{table}

@@

\begin{table}[H]
\caption{Expectation plaintiff against defendant part}
\label{Table_exp_plaintiff_def}
\begin{center}
\scriptsize{\input{./Tables/exp_plaintiff_def.tex}}
\end{center}
 \footnotesize
\textit{Notes:} 
The regression includes dummies of which party answered the survey (employee, employee's lawyer or firm) and if the lawyer is public or private. Pvalue1 refers to the p-value for the F-test \emph{ Emp-Public Lawyer=Emp Lawyer-Public Lawyer}, while Pvalue2 corresponds to \emph{ Emp-Public Lawyer=Emp Lawyer-Private Lawyer}
\textit{Do file: } \texttt{exp\_plaintiff\_def.do}
\end{table}

@@

%#appendix
\begin{table}[H]
    \caption{Treatment Effects by months after treatment (including basic variables controls)}
    \label{Table_effects}
    \begin{center}
    \scriptsize{\input{./Tables/minicortes_monthstreatment_B.tex}}
    \end{center}
    \footnotesize
    \textit{Notes:} 
    Calc=Conc and Calc=Conc=0 shows the p-value for the respective tests.
    \textit{Do file: } \texttt{minicortes\_monthstreatment.do}
\end{table}

@@

\begin{landscape}
\begin{table}[H]
    \caption{ITT and ATT (Scale Up)}
    \label{ITT_ATT}
    \begin{center}
    \scriptsize{\input{./Tables/ITT_ATT.tex}}
    \end{center}
    \footnotesize
    \textit{Notes:}

@@

\begin{figure}[H]
    \caption{Actor's expectations and calculator predictions.}
    \label{figlabel}
    \begin{center}
    \begin{subfigure}{0.49\textwidth}
        \caption{Employee}
        \centering
        \includegraphics[width=\textwidth]{Compensation_comparison_employee.pdf}
    \end{subfigure}
     \begin{subfigure}{0.49\textwidth}
        \centering
        \includegraphics[width=\textwidth]{Probability_comparison_employee.pdf}
    \end{subfigure}
    \begin{subfigure}{0.49\textwidth}
        \caption{Employee Lawyer}
        \centering
        \includegraphics[width=\textwidth]{Compensation_comparison_EmployeeLawyer.pdf}
        \end{subfigure}
          \begin{subfigure}{0.49\textwidth}
        \centering
        \includegraphics[width=\textwidth]{Probability_comparison_EmployeeLawyer.pdf}
    \end{subfigure}
        \begin{subfigure}{0.49\textwidth}
            \caption{Firm Lawyer}
            \centering
            \includegraphics[width=\textwidth]{Compensation_comparison_FirmLawyer.pdf}
    \end{subfigure}
    \begin{subfigure}{0.49\textwidth}
            \centering
            \includegraphics[width=\textwidth]{Probability_comparison_FirmLawyer.pdf}
        \end{subfigure}
    \end{center}
     \footnotesize \textit{Notes: Sample distributions for parties' expectations and calculator predictions.} Bandwidth for amount: 0.5 (log) pesos  Bandwidth for probability: 5\%. 
      \footnotesize{ \textit{Do file: }  \texttt{oc\_comparison.do}}
\end{figure}

\begin{figure}[H]
    \caption{Histograms of relative OC}
    \label{hist_rel_oc}
    \begin{center}
        \includegraphics[width=0.9\textwidth]{hist_rel_oc.pdf}
        \end{center}
        {\footnotesize \textit{Notes: Histograms of relative overconfidence in amount an d probability. Relative overconfidence is measured as $\frac{survey-calc}{calc}$. The histograms only display up to the 98 percentile.}}
        \texttt{hist\_rel\_oc.do}
\end{figure}

>>>>

\begin{table}[H]
    \caption{Baseline expectations comparison between parties - Pilot}
    \label{Table_expectations_plaintiff_defendant}
    \begin{center}
       \scriptsize{\input{./Tables/SS_B.tex}}
    \end{center}
    \footnotesize    
    \textit{Notes: Summary statistics on parties' beliefs, conditioning on having survey data for both parties. Since there are few observations for which both client and lawyer answered the survey, we take a simple average whenever that is the case.}

@@

%#include
\begin{table}[H]
    \caption{Amount asked (log), amount won (log), and probability of winning - Historic Data}
    \label{Table_Reg_winnings_log}
    \begin{center}
        \scriptsize{\input{./Tables/TableReg1_log.tex}}
    \end{center}
    \footnotesize
    \textit{Notes: Regression of amounts (in log pesos) asked (in log pesos) asked/won ratio and prob. of winning, by outcome (only basic variables included).} 
    \textit{Do file: } \texttt{reg\_amount.do}
\end{table}

@@

\begin{landscape}
%#include
\begin{table}[H]
\caption{Determinants of overconfidence - Pilot}
\label{Table_determinantsOC}
\begin{center}
\scriptsize{\input{./Tables/OC_reg.tex}}
\end{center}
 \footnotesize
\textit{Notes:} 
\emph{Mistreated} variable refers to the survey question: "How well do you think you were treated by the firm?". The omitted category is "Very Good", while 1, 2 and 3 refer to "Fairly Well", "Not so well" and "Not well at all".
Omited variable for \emph{education} is elementary education, while for \emph{Mistreated} is very good, and the scale is increasing, i.e. the worker feels more mistreated . We use a measure of relative overconfidence which is the \textit{percentage} quantity expected over the calculators prediction.
\textit{Do file: } \texttt{oc\_reg.do oc\_reg\_B.do}
\end{table}

@@

\begin{table}[H]
\caption{Determinants of updating (Theta) - Pilot}
\label{Table_determinants_updating}
\begin{center}
\scriptsize{\input{./Tables/update_reg_theta.tex}}
\end{center}
 \footnotesize
\textit{Notes:} All regressions include basic variables as controls, which are: Female, At will worker, Tenure, Daily wage, Weekly hours.
\emph{Mistreated} variable refers to the survey question: "How well do you think you were treated by the firm?". The omitted category is "Very Good", while 1, 2 and 3 refer to "Fairly Well", "Not so well" and "Not well at all".
Omited variable for \emph{education} is elementary education, while for \emph{Mistreated} is very good, and the scale is increasing, i.e. the worker feels more mistreated . Theta updating refers to the following statistic: $\theta=\left|\frac{P-exitsurvey}{P-initialsurvey}\right|$. Where $P$ is the prediction made by the calculator and $exit$ and $initial$ survey variables denote what each part answered on the survey for amount won. Note that when $\theta=1$ we have no update with respect to the prediction. And when $\theta<1$ they update in the direction of what calculator says. The extreme case $\theta=0$ implies perfect updating with respect to what the calculator says. 
\textit{Do file: } \texttt{update\_reg\_theta\_rel.do}
\end{table}

\begin{table}[H]
\caption{Determinants of updating (Relative) - Pilot}
\label{Table_determinants_updating}
\begin{center}
\scriptsize{\input{./Tables/update_reg_rel.tex}}
\end{center}
 \footnotesize
\textit{Notes:} 
\emph{Mistreated} variable refers to the survey question: "How well do you think you were treated by the firm?". The omitted category is "Very Good", while 1, 2 and 3 refer to "Fairly Well", "Not so well" and "Not well at all".
Omited variable for \emph{education} is elementary education, while for \emph{Mistreated} is very good, and the scale is increasing, i.e. the worker feels more mistreated. Relative updating is computed as $\frac{exitsurvey-initialsurvey}{initialsurvey}$.
\textit{Do file: } \texttt{update\_reg\_theta\_rel.do}
\end{table}
\end{landscape}

@@

%#include
\begin{table}[H]
    \caption{Treatment Effects by months after treatment - Pilot}
    \label{Table_effects_F}
    \begin{center}
    \scriptsize{\input{./Tables/minicortes_monthstreatment.tex}}
    \end{center}
    \footnotesize
    \textit{Notes:} 
    Calc=Conc and Calc=Conc=0 shows the p-value for the respective tests.
    \textit{Do file: } \texttt{minicortes\_monthstreatment.do}
\end{table}

@@

\begin{landscape}
\begin{table}[H]
    \caption{ITT and ATT - Scale Up}
    \label{ITT_ATT}
    \begin{center}
    \scriptsize{\input{./Tables/ITT_ATT.tex}}
    \end{center}
    \footnotesize
    \textit{Notes:}

@@

\begin{figure}[H]
    \caption{Percent that know main legal constitutional entitlement - Pilot}
    \label{Knowindemfig}
    \begin{center}
        \begin{subfigure}{0.49\textwidth}
            \caption{Employee claims to know}
            \centering
            \includegraphics[width=\textwidth]{Knows.pdf}
        \end{subfigure}
        \begin{subfigure}{0.49\textwidth}
            \caption{Employee correctly knows }
                \centering
                \includegraphics[width=\textwidth]{Correctly_knows.pdf}
        \end{subfigure}
        \end{center}
    {\footnotesize \textit{Notes: } This is based on the subject's answer to two questions: 7.01: "In case of an unjustified firing, the law grants you to get a severance pay stipulated in the Constitution. Do you know how many days of your salary does this account for?" and "7:02: How many days of your salary does this pay account for?". First panel correspond to the first question while second panel to the second one.}
    {\footnotesize \textit{Do file: } \texttt{knowledge\_emp.do}}
\end{figure}

\begin{figure}[H]
    \caption{Knowledge about their own claims in lawsuit - Pilot}
    \label{Knowtheirclaimsfig}
    \begin{center}
        \begin{subfigure}{0.49\textwidth}
            \caption{Const. compensation}
            \centering
            \includegraphics[width=\textwidth]{Compensation.pdf}
        \end{subfigure}
        \begin{subfigure}{0.49\textwidth}
            \caption{SARIMSS}
                \centering
                \includegraphics[width=\textwidth]{Insurance.pdf}
        \end{subfigure}
        \begin{subfigure}{0.49\textwidth}
            \caption{Reinstatement}
            \centering
            \includegraphics[width=\textwidth]{Reinstatement.pdf}
        \end{subfigure}
            \hfill
        \begin{subfigure}{0.49\textwidth}
            \caption{Overtime}
            \centering
            \includegraphics[width=\textwidth]{Extra_hrs.pdf}
        \end{subfigure}
        \begin{subfigure}{0.49\textwidth}
            \caption{End of year bonus}
            \centering
            \includegraphics[width=\textwidth]{Holiday_bonus.pdf}
        \end{subfigure}
            \hfill
        \begin{subfigure}{0.49\textwidth}
            \caption{Sunday bonus}
            \centering
            \includegraphics[width=\textwidth]{Sunday_bonus.pdf}
        \end{subfigure}
    \end{center} 
        \footnotesize \textit{Notes: Percentage of subjects who correctly answered to the question regarding elements of their claim, by type of benefit asked.}
        {\footnotesize \textit{Do file: }  \texttt{knowledge\_lawsuit.do}}
\end{figure}

\begin{figure}[H]
    \caption{Differences in claims and compensation by case file outcome - Historical Data}
    \label{claimsvsoutcomes}
    \begin{center}
        \includegraphics[width=0.7\textwidth]{Amountasked.tiff}
        \end{center}
    \footnotesize \textit{Notes: This graph shows the average amount (in thousand pesos) asked, won (overall and conditional on winning), minimum legal compensation, and minimum legal compensation plus lost wages, by outcome. The bottom legend shows the percentage of cases with each outcome for our database (N=5005). Note that, by definition, workers have no chance of recovery in drops and expiries. In our data, all settlements imply a positive recovery for the worker; finally, \textbf{for judgments, only 24\% of the time does the worker recover anything.}} 
    {\footnotesize \textit{Script: } \texttt{amount\_plots.R}}
\end{figure}

\begin{figure}[H]
    \caption{Delay of case by type of conclusion - Historic Data}
    \label{DurationFig}
    \begin{center}
        \includegraphics[width=0.7\textwidth]{Duracion.pdf}
        \end{center}
    {\footnotesize \textit{Notes: Length of the case (in years) , by conclusion. Naturally, laudos (adjudication cases) have much higher duration than settlement cases (convenios).}}
    {\footnotesize \textit{Do file: } \texttt{length\_case.do}}
\end{figure}

\begin{figure}[H]
    \caption{Difference in what actor says and calculator predicts in amount and probability. - Pilot}
    \label{Figure_overconfidence_exp}
    \begin{center}
    \begin{subfigure}{0.49\textwidth}
        \caption{Employee}
        \centering
        \includegraphics[width=\textwidth]{difference_amount_employee.pdf}
    \end{subfigure}
     \begin{subfigure}{0.49\textwidth}
        \centering
        \includegraphics[width=\textwidth]{difference_prob_employee.pdf}
    \end{subfigure}
    \begin{subfigure}{0.49\textwidth}
        \caption{Employee Lawyer}
        \centering
        \includegraphics[width=\textwidth]{difference_amount_employeelawyer.pdf}
        \end{subfigure}
          \begin{subfigure}{0.49\textwidth}
        \centering
        \includegraphics[width=\textwidth]{difference_prob_employeelawyer.pdf}
    \end{subfigure}
        \begin{subfigure}{0.49\textwidth}
            \caption{Firm Lawyer}
            \centering
            \includegraphics[width=\textwidth]{difference_amount_firmlawyer.pdf}
    \end{subfigure}
    \begin{subfigure}{0.49\textwidth}
            \centering
            \includegraphics[width=\textwidth]{difference_prob_firmlawyer.pdf}
        \end{subfigure}
    \end{center}
     \footnotesize \textit{Notes: Difference (in thousand pesos for amounts, percentage points for probabilities) from what the subject expects vs. what our models predict. Note how, for Employee and employee lawyer, the distribution for amounts is much more skewed to the right than for firm lawyers. This is only natural, since the formers are thinking about expected wins and the latters about expected losses.} 
      \footnotesize{ \textit{Do file: }  \texttt{oc\_comparison\_B.do}}
\end{figure}

\begin{figure}[H]
   \caption{Experiment flowchart - Pilot}
   \label{treatment_flowchart}
    \begin{center}
    \includegraphics[width=0.42\textwidth]{./Figuras/Experiment_flowchart.png}
    \end{center}
    \footnotesize
    \textit{Notes: this flowchart shows what happened when subjects arrived to the court.}
\end{figure}

\begin{figure}[H]
    \caption{Calculator treatment format (example) - Pilot}
    \label{calc_template}
    \begin{center}
        \includegraphics[width=0.9\textwidth]{calctreat.png}
        \end{center}
        {\footnotesize \textit{Notes: An example of the format shown to subjects in calculator treatment group. It shows some data on the worker, the minimum legal amount she deserves for different types of benefits, a small note on average trial duration, and calculator results: probability for each conclusion outcome, average duration and amount won (both conditional on each outcome).}}
\end{figure}

@@

\begin{table}[H]
    \caption{Summary statistics table by end mode - Historical Data}
    \label{tab:SS}
    \begin{center}
        \tiny{\input{./Tables/SS_bymodotermino.tex}}
    \end{center}
    \footnotesize
    \textit{Notes:} 
Summary stats of outcomes, basic and strategic variables by end mode.
    \textit{Do file: } \texttt{Table\_SS\_bymodotermino.do}
\end{table}

\begin{table}[H]
    \caption{Baseline Expectations - Pilot}
    \label{Table_expectations}
    \begin{center}
       \scriptsize{\input{./Tables/SS_A.tex}}
    \end{center}
    \footnotesize    
    \textit{Notes:} 
    Summary statistics of parties' beliefs. We show mean and standard deviation for the whole sample, \& dividing by type of employee's lawyer.
    \textit{Do file: } \texttt{Table\_SS.do  Table\_SS\_bylawyer.do}
\end{table}

@@

\begin{table}[H]
    \caption{Who showed up - Pilot}
    \label{whoshowedup}
    \begin{center}
        \scriptsize{\input{./Tables/Showed_up.tex}}
    \end{center}
    \footnotesize
    \textit{Notes:} 
We show some stats of who goes to the court. This is important since we can only give the treatment to the parties who go.  We decompose this in all the possible combination of show up: we use E,L,F,D subscripts to denote the different parties E: Employee; L: Employee’s Lawyer;  F: Firm; D: Firm’s Lawyer.
    \textit{Do file: } \texttt{showed\_up.do}
\end{table}

%#appendix
\begin{table}[H]
    \caption{Conciliation by type of lawyer- Pilot}
    \label{tab:reg_con_oc}
    \begin{center}
        \scriptsize{\input{./Tables/concilio_vs_lawyer.tex}}
    \end{center}
    \footnotesize
    \textit{Notes:} 
   Specification (1) refers to basic variables while (2) includes all strategic variables.
    \textit{Do file: } \texttt{con\_lawyer.do}
\end{table}

@@

%#appendix 
\begin{table}[H]
    \caption{Correlation conciliation vs overconfidence - Pilot}
    \label{Table_concvsoc}
    \begin{center}
        \scriptsize{\input{./Tables/Reg_con_oc.tex}}
    \end{center}
    \footnotesize
    \textit{Notes:} 
    All measures of OC are relative. Elastictity : Con-OC measures how much does conciliation change when overconfidence changes in 1 standard deviation. Elasticity SD:Con-OC measures how many standard deviations conciliation changes when  overconfidence changes in 1 standard deviation.
    \textit{Do file: } \texttt{corr\_con\_oc.do corr\_con\_oc\_B.do}
\end{table}

\begin{table}[H]
    \caption{Correlation conciliation vs theta update - Pilot}
    \label{Table_concvsoc_theta}
    \begin{center}
        \scriptsize{\input{./Tables/Reg_con_oc_theta.tex}}
    \end{center}
    \footnotesize
    \textit{Notes:} 
   We use the following statistic to measure updating: $\theta=\left|\frac{P-exitsurvey}{P-initialsurvey}\right|$. Where $P$ is the prediction made by the calculator and $exit$ and $initial$ survey variables denote what each part answered on the survey for amount won.. Elastictity : Con-OC measures how much does conciliation change when overconfidence changes in 1 standard deviation. Elasticity SD:Con-OC measures how many standard deviations conciliation changes when  overconfidence changes in 1 standard deviation.
    \textit{Do file: } \texttt{con\_vs\_oc\_theta.do}
\end{table}

@@

\begin{table}[H]
   \caption{Treatment description - Pilot}
    \label{treatment_description}
    \begin{center}
    \scriptsize{\input{./Tables/Experiment_description2.tex}}
    \end{center}
    \footnotesize
    \textit{Notes: This is a short description of the kind of treatment received by each treatment group.} 
\end{table}

@@

\begin{table}[H]
\caption{Expectation plaintiff against defendant part - Pilot}
\label{Table_exp_plaintiff_def}
\begin{center}
\scriptsize{\input{./Tables/exp_plaintiff_def.tex}}
\end{center}
 \footnotesize
\textit{Notes:} 
The regression includes dummies of which party answered the survey (employee, employee's lawyer or firm) and if the lawyer is public or private. Pvalue1 refers to the p-value for the F-test \emph{ Emp-Public Lawyer=Emp Lawyer-Public Lawyer}, while Pvalue2 corresponds to \emph{ Emp-Public Lawyer=Emp Lawyer-Private Lawyer}
\textit{Do file: } \texttt{exp\_plaintiff\_def.do}
\end{table}

@@

%#appendix
\begin{table}[H]
    \caption{Treatment Effects by months after treatment (including basic variables controls) - Pilot}
    \label{Table_effects}
    \begin{center}
    \scriptsize{\input{./Tables/minicortes_monthstreatment_B.tex}}
    \end{center}
    \footnotesize
    \textit{Notes:} 
    Calc=Conc and Calc=Conc=0 shows the p-value for the respective tests.
    \textit{Do file: } \texttt{minicortes\_monthstreatment.do}
\end{table}

@@

@@

\begin{figure}[H]
    \caption{Parties' expectations and calculator predictions. - Pilot}
    \label{figlabel}
    \begin{center}
    \begin{subfigure}{0.49\textwidth}
        \caption{Employee}
        \centering
        \includegraphics[width=\textwidth]{Compensation_comparison_employee.pdf}
    \end{subfigure}
     \begin{subfigure}{0.49\textwidth}
        \centering
        \includegraphics[width=\textwidth]{Probability_comparison_employee.pdf}
    \end{subfigure}
    \begin{subfigure}{0.49\textwidth}
        \caption{Employee Lawyer}
        \centering
        \includegraphics[width=\textwidth]{Compensation_comparison_EmployeeLawyer.pdf}
        \end{subfigure}
          \begin{subfigure}{0.49\textwidth}
        \centering
        \includegraphics[width=\textwidth]{Probability_comparison_EmployeeLawyer.pdf}
    \end{subfigure}
        \begin{subfigure}{0.49\textwidth}
            \caption{Firm Lawyer}
            \centering
            \includegraphics[width=\textwidth]{Compensation_comparison_FirmLawyer.pdf}
    \end{subfigure}
    \begin{subfigure}{0.49\textwidth}
            \centering
            \includegraphics[width=\textwidth]{Probability_comparison_FirmLawyer.pdf}
        \end{subfigure}
    \end{center}
     \footnotesize \textit{Notes: Sample distributions for parties' expectations and calculator predictions.} Bandwidth for amount: 0.5 (log) pesos  Bandwidth for probability: 5\%. 
      \footnotesize{ \textit{Do file: }  \texttt{oc\_comparison.do}}
\end{figure}

\begin{figure}[H]
    \caption{Histograms of relative OC - Pilot}
    \label{hist_rel_oc}
    \begin{center}
        \includegraphics[width=0.9\textwidth]{hist_rel_oc.pdf}
        \end{center}
        {\footnotesize \textit{Notes: Histograms of relative overconfidence in amount an d probability. Relative overconfidence is measured as $\frac{survey-calc}{calc}$. The histograms only display up to the 98 percentile.}}
        \texttt{hist\_rel\_oc.do}
\end{figure}
